Where and Why Does the Model Failed? A Visual Analytics Tool for Debugging, Tunning, and Interpreting Text Entailment Model

### 2018-02-19 paper/intro_entailVis.tex
update paper layout
update paper title

NLP application using attention
\begin{itemize}
    \item Neural translation
    \item Text summarization
    \item Text entailment
    \item Text comprehension (question answering)
\end{itemize

Attention type:
\begin{itemize}
    \item soft vs. hard
    \item local vs. global
    \item hierarchical
    \item attention over attention
    \item gated
\end{itemize}

>>>>

With the advances of deep learning, neural network based models have reset the state-of-the-art for nearly all linguistic tasks in natural language processing. The disruptive advance also brings enormous challenges. The opaque nature of neural network model leads to hard to debug system and difficult to interpret mechanism~cite{}. In this work, we use textual entailment task as an example to illustrate how a flexible visualization system can not only help NLP researchers quickly identify the potential limitation of a neural models and also probe the inner states of model for interpreting key mechanism such as attention.

(What is the high level motivation)

The importance of attention visualization.
For natural language processing application, the discrete nature of words and sentences presents additional challenge in interpreting the model. Recently, the advances in attention mechanism~\cite{} allow simpler models to match or even outperform more complex / deeper models by exploiting the alignment of bits of local text between sentences. The new challenges

% ####### Model Interpretability Section ##########
Making sense and explaining predictions made by deep neural networks is not only essential for validating and improving the model, but also becoming a necessity with increasing demands for model accountability (e.g., what is the evidence for making the decision) and model fairness (e.g., is the prediction affected by the bias in the training data).

However, investigating the inner mechanism of the model and explaining the model prediction is still an extremely challenging task.

% ######## Why use perturbation ###########
Iterate the model design and debug the system hinged on the ability to quickly and identify the errors made by a model.

Perturbe the input is what NLP researchers have subconsciously been doing to study and test a model.

Interpret/probe the relationship between attention and the prediction result

% NLP application using attention
% \begin{itemize}
%     \item Neural translation
%     \item Text summarization
%     \item Text entailment
%     \item Text comprehension (question answering)
% \end{itemize
%
%
% Attention type:
% \begin{itemize}
%     \item soft vs. hard
%     \item local vs. global
%     \item hierarchical
%     \item attention over attention
%     \item gated
% \end{itemize}

### 2018-02-19 paper/paper_entailVis.tex
update paper title

%% Paper title.
\title{How Alignment Impact Language Learning Tasks? \\ A Visual Analytics Tool
for Interpreting, Debugging, \\ and Tunning Text Entailment Model}

@@

%% Abstract section.
% What are we doing in this paper
\abstract{
With the advances of deep learning, neural network based models have reset
the state-of-the-art for nearly all linguistic tasks in natural language
processing. The disruptive advance also brings enormous challenges.
The opaque nature of neural network model leads to hard to debug system and
difficult to interpret mechanism~cite{}. In this work, we use textual
entailment task as an example to illustrate how a flexible visualization
system can help NLP researchers quickly identify the potential limitation of
a models and probe the model inner states for interpreting key mechanism
such as attention.
} % end of abstract

>>>>

%% Paper title.
\title{Where and Why Does the Model Failed? A Visual Analytics Tool for Debugging, Tunning, and Interpreting Text Entailment Model}

@@

%% Abstract section.
% What are we doing in this paper
\abstract{
With the recent advances of deep learning, neural network based models have reset
the state-of-the-art for nearly all linguistic tasks in natural language
processing. The disruptive advance also brings enormous challenges.
The opaque nature of neural network model leads to hard to debug system and
difficult to interpret mechanism~cite{}. In this work, we use textual
entailment task as an example to illustrate how a flexible visualization
system can help NLP researchers quickly identify the potential limitation of
a models and probe the model inner states for interpreting key mechanism
such as attention.
} % end of abstract

### 2018-02-19 paper/relatedWorks_entailVis.tex
add dependency tree to attenSen, but the parse tree compuation is duplicated
update paper title

Related works
\begin{itemize}
    \item Interacting with Predictions: Visual Inspection of Black-box Machine Learning Models,
    Use partial dependency (varying along one feature and observer how prediction changes)
    \item “Why Should I Trust You?” Explaining the Predictions of Any Classifier (LIME)

@@

>>>>

How to interpret classification task
\begin{itemize}
    \item What feature / dimension / part-of-the-input should change to
    alter the outcome
    \item What Examples can you provide that is similar to the current
    instance

@@

(Limitation of the state-of-the arts)
Model independent explanations is useful to gain intuition, but they lack the ability to link the external observation with inner states/mechanism of the model.

Papers:
\begin{itemize}
    \item Interacting with Predictions: Visual Inspection of Black-box Machine Learning Models,
    Use partial dependency (varying along one feature and observer how prediction changes)
    \item “Why Should I Trust You?” Explaining the Predictions of Any Classifier (LIME)
